---
title: "R-package_vignette - Andrew Muehr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{R-package_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This R-package contains four useful, documented functions that were used throughout this course, along with a documented data set. These functions largely pertain to plotting data and statistical relationships that require computational power to complete. However, there is one function that performs a simple probabilistic calculation. This vignette will demonstrate the usage of these four functions. First, we load the package (named "MATH4753") from our library. 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
knitr::opts_chunk$set(fig.width=7, fig.height=5) 
```

```{r setup}
library(MATH4753)
```

# 1. mynbin function

```{r}
MATH4753::mynbin(y = 10, r = 2, p = 0.5)

# This function is the most simple of the four in the package. It performs a standard binomial probability calculation, where y is the number of trials, r is the number of successes, and p is the probability of success.

# Use ?mynbin for more information 
```

# 2. myclt function

```{r}
a = MATH4753::myclt(n = 100, iter = 1000, a = 2, b = 8)
a[1]

# This function produces a histogram. n defines how many samples you wish to analyze, iter determines how many iterations the function will perform for n number of samples, while a and b determine the left and right bound of the n samples of the uniform distribution. 

# Use ?myclt for more information
```

# 3. myNRML function

```{r}
MATH4753::myNRML(x0=1,delta=0.001,llik=function(x)log(dpois(4,x)*dpois(6,x)*dpois(7,x)*dpois(6,x)*dpois(5,x)),xrange=c(0,10),parameter="param")

# The myNRML function graphically displays the work of the 
#Newton-Raphson graphical approach to finding the maximum likelihood. 
#Decreasing the value of delta (i.e. the "step") improves the accuracy 
#of this approach. This example is from Lab 10. 

# use ?myNRML for more information 
```

# 4. myboot2 function

```{r}
MATH4753::myboot2(iter = 1000000, x = 1000, fun = "mean", alpha = 0.05, cx = 1.5)

# This function creates a density histogram of the bootstrap sample statistics. You define the function that you wish to analyze. Increasing the value of iter will result in greater "accuracy." 


# Use ?myboot2 for more information
```
